---
title: "Image Renaming"
author: "Russell Dinnage"
date: "28/07/2014"
output: 
  html_document:
    highlight: pygments
---

```{r knitr_init, echo=FALSE, results="asis", cache=FALSE}
library(knitr)

## Global options
options(max.print="75")
opts_chunk$set(fig.path="out/",
               echo=TRUE,
         cache=TRUE,
               cache.path="cache/",
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75)
```

Here we will be trying to rename some image files, based on a nested directory structure that they are in. then we can get rid of the directory structure, which at the moment is the only thing identifying what sample the image copmes from (except for a label in the first image in the directory). First we can grab all of the image files names.

```{r list_files}
dir_name <- "/media/Kimberley-DataPhotos/5)\ Patch\ Sorted\ MP\ Photos-Checked"
img_files <- list.files(dir_name, recursive = TRUE, full.names = TRUE)
img_files[5000:5025]
```

There are two directories we don't need: `00_ColourCharts` and `00_Junk`. Let's remove those from the list.

```{r rm_junk}
img_files <- img_files[-grep("00_", img_files, fixed = TRUE)]
img_files <- img_files[-grep(".xmp", img_files, fixed = TRUE)] ## remove .xmp files
img_files <- img_files[-grep("Renamed", img_files, fixed = TRUE)] ## already renamed files
img_files[1:50]
```

We need to collect the date information from the files, because later we need to sort the files by date within each sample label.

```{r collect_dates}
file_dat <- file.info(img_files)$mtime
file_dat[1:50]
```

We can remove the redundant base directory from each of these.

```{r rm_names}
img_names <- gsub("/media/Kimberley-DataPhotos/5) Patch Sorted MP Photos-Checked/", "", img_files)
img_names[1:50]
length(img_names)
```

There are `r length(img_names)` images to be processed. We can create the properly formatted filenames using the packages `tidyr` and `dplyr`, and some string manipulation.

```{r tidy_names}
library(tidyr)
library(dplyr)
img_data <- data.frame(file_name = img_names) %>% separate(file_name, c("Patch", "Location", "Direction", "Filename"), "/", remove = FALSE) %>% separate(Filename, c("Filename","Extension"), "\\.") %>% mutate(Date = file_dat) %>% tbl_df
img_data
```

The format of the filenames goes like this M\<patch\>\<location\>\<direction\>-\<col\>\<row\>-\<filetype\>.\<ext\>, where \<patch\> looks like 5-1, instead of 05_1. \<col\> and \<row\> are the column and row of the image on the tray. These should go in order starting with column A, and going through rows 1 - 4. We'll start by stripping leading zeroes and then reordering the images by date and time within each patch, location, direction combination.

```{r rorder}
img_data$Patch <- gsub("^0", "", img_data$Patch)
img_data$Patch <- gsub("_", "-", img_data$Patch, fixed = TRUE)
img_data
img_data <- img_data %>% arrange(Patch, Location, Direction, Extension, Date)
img_data %>% select(-file_name)
```

We will set up a vector with the right -\<col\>\<row\>-\<filetype\>.\<ext\> values in order. Then we can just concatenate everything together.

```{r concat}
file_ends <- list()
file_ends[["JPG"]] <- c("-A1-J.jpg", "-A2-J.jpg", "-A3-J.jpg", "-A4-J.jpg", "-B1-J.jpg", "-B2-J.jpg", "-B3-J.jpg", "-B4-J.jpg", "-C1-J.jpg", "-C2-J.jpg", "-C3-J.jpg", "-C4-J.jpg", "-D1-J.jpg", "-D2-J.jpg", "-D3-J.jpg", "-D4-J.jpg", "-A1-J2.jpg", "-A2-J2.jpg", "-A3-J2.jpg", "-A4-J2.jpg", "-B1-J2.jpg", "-B2-J2.jpg", "-B3-J2.jpg", "-B4-J2.jpg", "-C1-J2.jpg", "-C2-J2.jpg", "-C3-J2.jpg", "-C4-J2.jpg", "-D1-J2.jpg", "-D2-J2.jpg", "-D3-J2.jpg", "-D4-J2.jpg")
file_ends[["CR2"]] <- c("-A1-R.cr2", "-A2-R.cr2", "-A3-R.cr2", "-A4-R.cr2", "-B1-R.cr2", "-B2-R.cr2", "-B3-R.cr2", "-B4-R.cr2", "-C1-R.cr2", "-C2-R.cr2", "-C3-R.cr2", "-C4-R.cr2", "-D1-R.cr2", "-D2-R.cr2", "-D3-R.cr2", "-D4-R.cr2", "-A1-R2.cr2", "-A2-R2.cr2", "-A3-R2.cr2", "-A4-R2.cr2", "-B1-R2.cr2", "-B2-R2.cr2", "-B3-R2.cr2", "-B4-R2.cr2", "-C1-R2.cr2", "-C2-R2.cr2", "-C3-R2.cr2", "-C4-R2.cr2", "-D1-R2.cr2", "-D2-R2.cr2", "-D3-R2.cr2", "-D4-R2.cr2")
img_data_new <- img_data %>% group_by(Patch, Location, Direction, Extension) %>% mutate(N = row_number()) %>%
  rowwise %>% mutate(Ends = file_ends[[Extension]][N]) %>%
  mutate(FullName = sprintf("M%s%s%s%s", Patch, Location, Direction, Ends))
img_data_new$FullName
```

Now at last we can copt and rename the files.

```{r copy_rename, eval=FALSE}
old_files <- paste0("/media/Kimberley-DataPhotos/5) Patch Sorted MP Photos-Checked/",
                    img_data_new$file_name)
new_files <- paste0("/media/Kimberley-DataPhotos/5) Patch Sorted MP Photos-Checked/Renamed/",
                    img_data_new$FullName)
file.copy(old_files, new_files, copy.date = TRUE)
```
